Supplement

### 2023-07-05 paper/manuscript.Rmd
work

 Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions. Yet in psychology, some prominent individual findings have failed to replicate in multi-site replication attempts [ex. terror management theory, @klein2022; ego-depletion, @hagger2016], and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40% [@openscienceconsortium2015]. When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result. As each failed extension does not directly contradict the original result, many scientists may waste a lot of time and resources pursuing results where there may be none.

To identify studies are risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability. Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.

 [Prior paragraph may still need work]

@@

While their sampling and methods varied, these previous approaches to replicability have focused on interpreting their results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable. Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample [@vanbavel2016] or even time period [@ramscar]. Further, the methods for estimating this quantity have been theoretically problematic. Sampling schemes did not reflect an entirely random sample from the literature; instead replication projects sampled from specific journals where results may be of more interest and adjusted the sample for feasibility concerns. These are reasonable sampling choices, but they undermine the claim that the estimand is the level of "truth" in the literature as a whole. Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true [@wilson2020]. The importance of a study being replicable is not uniformly distributed across the literature.

[Prior paragraph is a bit verbose, but it's probably fine]

Rather than aim for some measure of "true" replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures. With this lens, we could say that RP:P looked at how well findings in well-known journals can be replicated in a typical psychology lab. Many Labs looked at which well-known two conditions studies replicate with huge samples, and @camerer2018 looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement. All of these are potentially desirable estimands depending on what the specific circumstances and questions of interest are.

@@

Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science. If a study cannot be replicated in a given set of circumstances, we believe it it unlikely that the study can be successfully built upon in those circumstances either. Thus, we look at what studies are replicable under the circumstances where most scientific work is conducted: by students who are working with limited budgets, limited time, and without access to outside experts [@frank2012]. Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.

>>>>

 Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions. Yet in psychology, some prominent individual findings have failed to replicate in multi-site replication attempts [ex. terror management theory, @klein2022; ego-depletion, @hagger2016], and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40% [@openscienceconsortium2015]. When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result. As each failed extension does not directly contradict the original result, many scientists may waste considerable time and resources pursuing results where there may be none.

To identify studies at risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability. Measuring replicability has been the focus of much prior work, but there is limited consensus on what exactly is being estimated.

@@

While their sampling and methods varied, these previous approaches to replicability have focused on interpreting their results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable. Critics have pointed out that "true" replicability may not be possible to estimate outside of a specific sample [@vanbavel2016] or even time period [@ramscar]. Further, the methods for estimating this quantity have been theoretically problematic. Sampling schemes did not reflect an entirely random sample from the literature; instead replication projects sampled from specific journals where results may be of more interest and adjusted the sample for feasibility concerns. These are reasonable sampling choices, but they undermine the claim that the estimand is the level of "truth" in the literature as a whole. Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true [@wilson2020].

Rather than aim for some measure of "true" replicability, it makes more sense to contextualize replication efforts based on their methodologies and outcome measures. With this lens, we could say that RP:P looked at how well findings in well-known journals can be replicated in a typical psychology lab. Many Labs looked at which well-known two condition studies replicate with huge samples, and @camerer2018 looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement. All of these are potentially desirable estimands depending on what the specific circumstances and questions of interest are.

@@

In practice, most scientific work is not conducted 
Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science. If a study cannot be replicated in a given set of circumstances, we believe it it unlikely that the study can be successfully built upon in those circumstances either. Thus, we look at what studies are replicable under the circumstances where most scientific work is conducted: by students who are working with limited budgets, limited time, and without access to outside experts [@frank2012]. Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.

### 2023-07-05 paper/supplement.Rmd
work

@@

tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(type="Without stats predictors") |> mutate(sens="All data")
tier2_porig <- read_rds(here(model_location, "tier2_porig.rds"))|> do_draws() |>  mutate(type="Without stats predictors") |> mutate(sens="All data")
tier2_predint <- read_rds(here(model_location, "tier2_predint.rds"))|> do_draws() |>  mutate(type="Without stats predictors") |> mutate(sens="All data")
tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |> mutate(type="Stats predictors") |> mutate(sens="All data")
tier3_porig <- read_rds(here(model_location, "tier3_porig.rds"))|> do_draws() |>  mutate(type="Stats predictors") |> mutate(sens="All data")
tier3_predint <- read_rds(here(model_location, "tier3_predint.rds"))|> do_draws() |>  mutate(type="Stats predictors") |> mutate(sens="All data")

sens1_subjective <- read_rds(here(model_location, "sens_tier1_subjective.rds"))|> do_draws() |> mutate(type="Without stats predictors") |> mutate(sens="Sensitivity test")
sens2_porig <- read_rds(here(model_location, "sens_tier2_porig.rds"))|> do_draws() |> mutate(type="Without stats predictors")|> mutate(sens="Sensitivity test")
sens2_predint <- read_rds(here(model_location, "sens_tier2_predint.rds"))|> do_draws() |> mutate(type="Without stats predictors")|> mutate(sens="Sensitivity test")
sens3_subjective <- read_rds(here(model_location, "sens_tier3_subjective.rds"))|> do_draws()|> mutate(type="Stats predictors")|> mutate(sens="Sensitivity test")
sens3_porig <- read_rds(here(model_location, "sens_tier3_porig.rds"))|> do_draws()|> mutate(type="Stats predictors")|> mutate(sens="Sensitivity test")
sens3_predint <- read_rds(here(model_location, "sens_tier3_predint.rds"))|> do_draws()|> mutate(type="Stats predictors")|> mutate(sens="Sensitivity test")

@@

# tau**2  sensitivity analysis is a mess

@@

d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> count(predInt)

#of those with SMD predInts
d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> count(predInt)
d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> count(predInt_from_d)
d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> count(predInt_with_tau)

d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> summarise(median(p_orig))
#median .03

#of those with SMD predInts
d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |>summarise(median(p_orig))
d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_from_d))
d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_with_tau))
```

>>>>

\pagebreak

@@

tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds")) |> do_draws() |> mutate(type="All original-replication pairs") |> mutate(sens="All data")
tier2_porig <- read_rds(here(model_location, "tier2_porig.rds"))|> do_draws() |>  mutate(type="All original-replication pairs") |> mutate(sens="All data")
tier2_predint <- read_rds(here(model_location, "tier2_predint.rds"))|> do_draws() |>  mutate(type="All original-replication pairs") |> mutate(sens="All data")
tier3_subjective <- read_rds(here(model_location, "tier3_subjective.rds"))|> do_draws() |> mutate(type="Only pairs with full statistical info") |> mutate(sens="All data")
tier3_porig <- read_rds(here(model_location, "tier3_porig.rds"))|> do_draws() |>  mutate(type="Only pairs with full statistical info") |> mutate(sens="All data")
tier3_predint <- read_rds(here(model_location, "tier3_predint.rds"))|> do_draws() |>  mutate(type="Only pairs with full statistical info") |> mutate(sens="All data")

sens1_subjective <- read_rds(here(model_location, "sens_tier1_subjective.rds"))|> do_draws() |> mutate(type="All original-replication pairs") |> mutate(sens="Sensitivity test")
sens2_porig <- read_rds(here(model_location, "sens_tier2_porig.rds"))|> do_draws() |> mutate(type="All original-replication pairs")|> mutate(sens="Sensitivity test")
sens2_predint <- read_rds(here(model_location, "sens_tier2_predint.rds"))|> do_draws() |> mutate(type="All original-replication pairs")|> mutate(sens="Sensitivity test")
sens3_subjective <- read_rds(here(model_location, "sens_tier3_subjective.rds"))|> do_draws()|> mutate(type="Only pairs with full statistical info")|> mutate(sens="Sensitivity test")
sens3_porig <- read_rds(here(model_location, "sens_tier3_porig.rds"))|> do_draws()|> mutate(type="Only pairs with full statistical info")|> mutate(sens="Sensitivity test")
sens3_predint <- read_rds(here(model_location, "sens_tier3_predint.rds"))|> do_draws()|> mutate(type="Only pairs with full statistical info")|> mutate(sens="Sensitivity test")

@@

\pagebreak

# Heterogeneity analysis

@@

all_true <- d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> filter(predInt) |> nrow()

all <- d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> nrow()

#of those with SMD predInts
all_orig  <- d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> nrow()
all_orig_true <- d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt) |> nrow()
all_d_true <- d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt_from_d) |> nrow()
all_tau <- d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> filter(predInt_with_tau) |> nrow()

The prediction interval and p-original values used for models and point estimates were done on the original scale where possible. However, to do heterogeneity analysis, our imputed value for tau is in SMD units, so we have to use SMD units for the original and replication values. This limits the number of applicable original-replication pairs. Prediction intervals are sensitive to whether only studies with SMD are included (different studies report differently and also vary in how close replications were) and whether the scale used was original or SMD (if the variances differed between original and replication).

Of all studies where prediction intervals can be calculated, `r all_true`/`r all` (`r round(all_true/all*100)`%) of the original estimates had prediction intervals that included the replication effect size. For those where we have SMD, `r all_orig_true`/`r all_orig` (`r round(all_orig_true/all_orig*100)`%) of the original estimates had prediction intervals that included the replication effect size, when we use original units where possible.  Using SMD units, `r all_d_true`/`r all_orig` (`r round(all_d_true/all_orig*100)`%) of the original estimates had prediction intervals that included the replication effect size. Allowing for heterogeneity, with tau=.21, `r all_tau`/`r all_orig` (`r round(all_tau/all_orig*100)`%) of the original estimates are distributionally consistent.
